Three-dimensional binary-liquid lattice Boltzmann simulation of microchannels with rectangular cross sections

### 2011-09-22 Text/Submission/paper.tex
Started doing the referee report.

The binary liquid free-energy LB model due to \citet{swift} that we used
simulates two liquids with the assumption of uniform overall
density. %As it was indicated by \citet{gupta-review} a flow in microchannels is a complex
%interplay of viscous, gravitational, inertial and surface forces. 
The classical Bretherton
problem is stated for gas and liquid, which are of
significantly
different density and viscosity. However, the numerical results of
\citet{giavedoni-numerical} and \citet{heil-bretherton} show
negligible Reynolds number effects on the film thickness for a relatively wide range of Reynolds
numbers, $Re<70$. The parameters in our simulations were carefully chosen to
avoid  inertia
effects, see Section \ref{sec:numerical:benchmark}. The maximum attained
Reynolds number $Re<10$. Thus, inertia effects can be neglected. Therefore, a major governing
factor for microchannel flows is not the density ratio, but
the
viscosity ratio. As a result, the uniform density binary liquid model is suitable for this kind of
simulations.  
% THIS HAS ALREADY BEEN STATED BEFORE
% The goal of this work is to do a feasibility study of the LBM
% binary-liquid model to simulate and correctly predict flow patterns for the Bretherton/Taylor
% problem.

>>>>

The binary liquid free-energy LB model due to \citet{swift} that we used
simulates two liquids with the assumption of uniform overall
density. %As it was indicated by \citet{gupta-review} a flow in microchannels is a complex
%interplay of viscous, gravitational, inertial and surface forces. 
The classical Bretherton
problem is stated for gas and liquid, which are of
significantly
different density and viscosity. {\color{red} The system is simulated in a right manner if all
non-dimensional parameters are matched in real physical system and simulation system.
However, one needs to consider the leading non-dimensional numbers which are responsible for
physical phenomenon. Even, the binary-liquid model cannot match the gas-liquid density ratio, we
consider it as a non-leading parameter. First of all, the numerical
results of
\citet{giavedoni-numerical} and \citet{heil-bretherton} show
negligible Reynolds number effects on the film thickness for a relatively wide range of Reynolds
numbers, $Re<70$. The parameters in our simulations were carefully chosen to
avoid  inertia
effects, see Section \ref{sec:numerical:benchmark}. The maximum attained
Reynolds number $Re<10$. The second reason is that density ratio is involved while describing a
bubble shape change. There is a corresponding number defining the shape change, Bond number. Bond
number is $Bo=\frac{Ca\,Re}{Fr^2}$. For real microchannel systems the Bond number is less than
$Bo<0.1$ and we can neglect a bubble shape change.}
Therefore, a major governing
factor for microchannel flows is not the density ratio, but
the
viscosity ratio. As a result, the uniform density binary liquid model is suitable for this kind of
simulations.  
% THIS HAS ALREADY BEEN STATED BEFORE
% The goal of this work is to do a feasibility study of the LBM
% binary-liquid model to simulate and correctly predict flow patterns for the Bretherton/Taylor
% problem.
